---
output: "github_document"
bibliography: "references.bib"
link-citations: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# honos

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

<!-- badges: end -->

The goal of the `honos` R package is to assist with the analysis and visualisation of Health of the Nation Outcome Scales (HoNOS) [@Wing1998].

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CDU-data-science-team/honos")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(honos)
## basic example code
```


## Datasets

The package comes with a simulated datasets of HoNOS scores (13-items) that is available in "long" as well as "wide" format.

### Long format

- `id`: Unique identifier 
- `date`: Date variable
- `measure`: Description of measure
- `item`: Number of HoNOS item
- `value`: HoNOS score

```{r}
honos_long %>% 
  dplyr::filter(id %in% paste0("id", 1:5))
```

### Wide format

- `id`: Unique identifier 
- `date`: Date variable
- `measure`: Description of measure
- `honos_i1` to `honos_i13`: HoNOS score for each item

```{r}
honos_wide %>% 
  dplyr::filter(id %in% paste0("id", 1:5))
```


## Resources

- https://www.rcpsych.ac.uk/events/in-house-training/health-of-nation-outcome-scales
- https://www.nhs.uk/Scorecard/Pages/IndicatorFacts.aspx?MetricId=9308
- https://www.healthylondon.org/resource/mental-health-in-integrated-care-systems/outcome-measures/honos/

## References
