---
title: "Describe HoNOS items, severity scores, and clusters"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{describe_honos}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Describe HoNOS item labels

- `as_item_desc()`: Add item descriptions (For 13 and 18 item versions of the HoNOS)
 
```{r}
library(honos)

honos_long %>% 
  dplyr::mutate(item_desc = as_item_desc(item, n_items = 13))

```
In item 8, the clinician can specify 10 different categories.
The function `as_i8_desc()` can be used to add more detailed labels, for example:

```{r}
as_i8_desc("B")
```


## Describe HoNOS severity scores

- `as_severity_desc()`: Add severity descriptions (Values '0' to '4')

```{r}
library(honos)

honos_long %>% 
  dplyr::mutate(value_desc = as_severity_desc(value, na_level = "I AM A MISSING VALUE"))

```
## Describe clusters

- `as_cluster_desc()`: Describe clusters (Values: 0 to 21)

```{r}

library(honos)
x <- 0:21
as_cluster_desc(x)

```

