---
title: "Example HoNOS datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example_honos_datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Datasets

The package comes with a simulated dataset of HoNOS scores in "wide" format.
A helper function can be used to transform this data into "long" format (`pivot_honos_longer`).

```{r}
library(honos)

honos_data
```

Although the original variable names in `honos_data` are somewhat self-explanatory, they are not good! 
Therefore this package also offers a function to rename the variables (`rename_honos()`) to be more consistent and allow for easier further data manipulation.

```{r}

honos_data %>% 
  rename_honos(value_vars_current = c("q1", "q2", "q3", "q4", "q5", "q6", "q7", 
                                      "q8", "q9", "q10", "q11", "q12", "q13"),
               prob_var_item8 = c("q8_prob"),
               spec_var_item8 = c("q8_spec"),
               value_vars_history = c("qa", "qb", "qc", "qd", "qe"))

```


### Create long data set

There are two options to create a long data set:

1. Create a long data set that includes item 8 problem description and additional specification variables `pivot = "all_items"`

```{r}

honos_long <- honos_data %>% 
  pivot_honos_longer(value_vars_current = c("q1", "q2", "q3", "q4", "q5", "q6", "q7", 
                                            "q8", "q9", "q10", "q11", "q12", "q13"),
                     prob_var_item8 = c("q8_prob"),
                     spec_var_item8 = c("q8_spec"),
                     value_vars_history = c("qa", "qb", "qc", "qd", "qe"), 
                     pivot = "all_items")

honos_long

```

2. Create a long data set with that includes only scores in long format  `pivot = "item_scores"`

```{r}

honos_longish <- honos_data %>% 
  pivot_honos_longer(value_vars_current = c("q1", "q2", "q3", "q4", "q5", "q6", "q7", 
                                            "q8", "q9", "q10", "q11", "q12", "q13"),
                     prob_var_item8 = c("q8_prob"),
                     spec_var_item8 = c("q8_spec"),
                     value_vars_history = c("qa", "qb", "qc", "qd", "qe"), 
                     pivot = "item_scores")

honos_longish
```
